---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
comment = NA, fig.width = 6, fig.height = 4, cache = FALSE)
```

# ggshredR

Colour palettes and plotting themes for shredR 80s guitar theme. Incredible example below of ![Racer X](https://www.google.com/search?q=racer+x+band&source=lnms&tbm=isch&sa=X&ved=2ahUKEwiJ_J_5yuvoAhUG4jgGHdZ5ABwQ_AUoAXoECBYQAw&biw=1440&bih=821#imgrc=5Us47XXgwbdo8M)

## Installation

You can install `ggshredR` from GitHub by running the following:

```{r eval = FALSE}
devtools::install_github("hendersontrent/ggshredR")
```

## Theme shredR

The theme works by adding the function call to the end of your `ggplot2` code:

```{r message = FALSE}
library(ggplot2)
library(ggshredR)

ggplot(mpg, aes(x = cyl, y = cty)) +
  geom_point(size = 3) +
  labs(title = "Cylinders vs city miles per gallon") +
  theme_shredR(grids = TRUE)
```

The colour palette built into the package is presented below:

```{r message = FALSE}
library(scales)

scales::show_col(ggshredR:::shredR_palette)
```

## This palette can be used for colouring (and filling) plots

Use `scale_colour_shredR()` to apply the theme for colour parameters.

```{r}
ggplot(mpg, aes(x = cyl, y = cty, colour = drv)) +
geom_point(size = 3) +
labs(title = "Cylinders vs city miles per gallon by drivetrain") +
scale_colour_shredR() +
theme_shredR(grids = TRUE)
```

And `scale_fill_shredR()` to apply the theme for fill parameters.

```{r message = FALSE}
library(dplyr)
library(magrittr)

mpg %>%
group_by(drv) %>%
summarise(cty = mean(cty)) %>%
ungroup()%>%
ggplot(aes(x = reorder(drv, -cty), y = cty, fill = drv)) +
geom_col() +
labs(title = "Average city miles per gallon by drivetrain") +
scale_fill_shredR() +
theme_shredR()
```
